%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.7in,top=0.6in,right=0.7in,bottom=0.6in]{geometry} % Document margins
\usepackage{fancyhdr}
\usepackage[english,printdayoff]{isodate}
\isodash{-}%
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newif\ifpublic{}
% by default it is set to false
\publicfalse{}

\makeatletter
\def\myrev{Next Review Date:}
\def\ps@lastpage{%
  \let\@oddhead\@empty\let\@evenhead\@empty%
  \def\@oddfoot{{\slshape\myrev}\hfil\thepage}%
  \def\@evenfoot{{\slshape\myrev}\hfil\thepage}%
  }
\makeatother


\name{Simone Perriello} % Your name
\begin{document}
\ifpublic{%
    \begin{mytabular}
      \row{Academic email}{simone.perriello@polimi.it}
    \end{mytabular}%
  }
\else{%
    \begin{mytabular}
      % \row{Date of Birth}{July, 25th 1989}
      % \row{Citizenship}{Italian}
      \row{Academic email}{simone.perriello@polimi.it}
      % \row{Personal email}{simone.perriello@protonmail.com}
      \row{Personal email}{sperriello@proton.me}
      \row{Github page}{github.com/tigerjack}
      % \row{Phone number}{(+39)3925266101}
      \row{Website}{https://perriello.faculty.polimi.it}
    \end{mytabular}%
  }
\fi

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
% PHD
\textbf{Ph.D. Candidate} \hfill \textit{since November 2019}
\\ Enrolled in Ph.D program in Information Technology at Politecnico di Milano 
\\ Thesis title: \textit{Quantum Computing Algorithms for Cryptography: design, validation and complexity assessment}
\\ Advisor Prof.\ \textit{Gerardo Pelosi}; Co-Advisor Prof.\ \textit{Alessandro Barenghi}
\\
\\
% MASTER
\textbf{M.Sc.\ degree} \hfill \textit{April 2019} 
\\ Master of Science in Computer Science and Engineering at Politecnico di Milano
\\ Thesis title: \textit{Design and developments of quantum circuits to solve the Information Set Decoding problem}
\\ Advisor Prof.\ \textit{Gerardo Pelosi}; Co-Advisor Prof.\ \textit{Alessandro Barenghi}; Grade: 110/110
\\
\\
% IELTS
\textbf{IELTS} \hfill \textit{February 2016}
\\ Grade 7.5/9 (equivalent to C1 of the CEFR)
\\
\end{rSection}
%--------------------------------------------------------------------------------
%    RESEARCH
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Research interests}
  My research lies at the intersection of the \textbf{quantum computing} and the
  \textbf{cryptography} fields. In the last years, I have been focusing on the
  design and development of quantum algorithms to attack code-based
  cryptosystems, undermining their alleged security.

  During my Ms.C. thesis, I designed a quantum version of the classical
  Information Set Decoding (ISD) strategy, the most efficient kind of attack
  against cryptosystems based on linear codes. The proposed algorithm was
  implemented and tested with linear codes of various types and sizes using the
  IBM's Qiskit framework. In doing so, as the Qiskit contributor list attests, I
  implemented a few patches for the Aqua framework.

  During my 6 months as an intern at Atos, I mainly focused on improving the
  simulation capabilities of algorithms targeting Noisy Intermediate-Scale
  Quantum (NISQ) architectures. In doing so, I developed a new general-purpose
  quantum simulation library from scratch that, by trading off simulation time
  and simulation space, was capable of simulating hundred of qubits and to
  replicate the experimental results shown by \textbf{Cerezo et al. 2020}.

  My Ph.D.\ research activities revolve around the \textbf{quantum
    cryptanalysis} of Post-Quantum Cryptography (\textbf{PQC}). Notably, one of
  the major quest in the quantum and cryptography communities is the assessment
  of new cryptographic standards capable of resisting to attacks from quantum
  accelerated computers. The search is witnessed by the call for standard borne
  out by the National Institute of Standards and Technology (\textbf{NIST}),
  that is expected to lead to draft of standards by the end of 2023. For this
  reason, I conducted practical evaluations in terms of circuit width and depth
  of the computational complexity required to attack all the code-based
  finalists of the NIST competition. An exhaustive comparison against both
  theoretical and concrete previous implementations testified that my quantum
  algorithms decreased the security level of all cryptoschemes by 19 to 30 bits.
  In the process, I exploited the several implementations of the \textbf{Dicke}
  state carried out by \textbf{B{\"a}rtschi}, and I also implemented several
  quantum circuits that can be of unrelated interests --- to sort bitstrings, to
  permute matrix columns, to perform Gauss-Jordan Elimination on a matrix, and
  to check the weight of a given bitstring.

  % In the same work, I
  % also presented different techniques to parallelize the algorithms across
  % multiple Quantum Processing Unitss. In doing so, I confirmed the concerns
  % brought forward by the latest NIST report on the security of one of the
  % proposed cryptoschemes when a parallel approach is used.

  % Finally, the quantification of the speed-up attainable in solving problems which remain computationally hard even with a quantum computer being available (e.g., problems characterizing cryptanalytic tasks, such as the subset sum problem), will be tackled.

% today is around algorithms for Noise
% %%%%
% The research activity will focus on the following topics: the development of new quantum algorithms, the analysis of their complexity, practical feasibility and scalability on the Quantum Learning Machine provided by AtoS, and applications of quantum techniques to problems in classical computer science and mathematics.

% Currently, it is an open question if quantum heuristics can outperform classical approximation techniques. Aiming to advance the state-of-the-art, the investigation will start from the study of the Quantum Approximate Optimization Algorithms (QAOA), to efficiently solve combinatorial optimization problems with the aid of quantum computers.

% Given the interest in the research community for quantum computer technologies, named Noisy Intermediate-Scale Quantum (NISQ), having 50 qubits or more and not equipped with fully developed error correction mechanisms, the said optimization algorithms will be tackled to fit also computations in the NISQ technology.

% Finally, the quantification of the speed-up attainable in solving problems which remain computationally hard even with a quantum computer being available (e.g., problems characterizing cryptanalytic tasks, such as the subset sum problem), will be tackled.

% %%%%
% In recent times, I am investigating the power of quantum computers, with a special 
% focus on cryptography. For my master thesis, I learned how to use the Qiskit 
% framework, proposing patches to Aqua. 

% I have extensively use Qiskit to implement several quantum circuits to solve
% the Information Set Decoding problem, one of the key aspects of post-quantum
% cryptography.

% While waiting to invest all the energies on my Ph.D. research on quantum computing,
% I am working as an intern at Atos. These months of work helped me to consolidate
% my knowledge on the topic, to see the state of the art of quantum simulation and to
% test all the new improvements made to the QLM project.
\end{rSection}
\clearpage
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
% \begin{rSection}{Technical Strengths}
% % PYTHON
% % QUANTUM
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Modeling and Analysis \ & AutoCad, Revit, StaadPro \\
% Software \& Tools & MS Office, Latex \\
% \end{tabular}
% 
% \end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
% NOTE Dates are in US format
\begin{rSection}{Work Experience}
% R&D Bull SAS
% \begin{rSubsection}{Atos: Bull SAS R\&D Labs}{February 2020--July 2020}{Quantum computing researcher}{Les Clayes-sous-Bois}
  \begin{rSubsection}{Atos: Bull SAS R\&D Labs}{\origdate\daterange{2020-02-01}{2020-07-31}}{Quantum computing researcher}{Les Clayes-sous-Bois}
\item Researched and explored state-of-the-art quantum algorithms and technologies, under the direct supervision of Bertrand Marchand and Cyril Allouche. 
\item Tested and implemented the algorithms on the \textit{Atos Quantum Learning Machine} simulator.
\end{rSubsection}

% ATOS QUANTUM
% \begin{rSubsection}{Atos: HPC \& Quantum team}{July 2019--January 2020}{Quantum computing researcher}{Milano}
\begin{rSubsection}{Atos: HPC \& Quantum team}{\origdate\daterange{2019-07-01}{2020-01-31}}{Quantum computing researcher}{Milano}
\item Configured both the hardware and software of the \textit{Atos Quantum Learning Machine} appliance.
\item Used the \textit{Atos Quantum Learning Machine} software simulation stack to develop well-known quantum algorithms.
\item Taken internal courses on the advanced usage of the \textit{Atos Quantum Learning Machine}.
\item Lectured external customers on the \textit{Atos Quantum Learning Machine} software stack.
\end{rSubsection}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------
\begin{rSection}{Teaching Experience}

  \begin{rSubsection}{Teaching assistant}{2021-22;\ 22-23}{Informatica (per Aerospaziali)}{Prof.\ Gerardo Pelosi}
  \item Exercise lectures: computer science for Aerospace Engineering.
  \item Topics addressed (partial): Boolean logic and basics of C programming.
  \end{rSubsection}
  \begin{rSubsection}{Teaching assistant}{2020-21;\ 21-22;\ 22-23}{Computer Architectures and Operating Systems}{Prof.\ Gerardo Pelosi}
  \item Exercise lectures: Linux Operating Systems.
  \item Topics addressed (partial): parallel programming (processes, threads),
    task scheduler, system calls and interrupt routines, memory management, file
    systems and I/O.
  \end{rSubsection}
  \begin{rSubsection}{Teaching assistant}{2022-23}{Computer Architectures and
      Operating Systems}{Prof.ssa Cristina Silvano }
  \item Exercise lectures: Linux Operating Systems.
  \item Topics addressed (partial): parallel programming (processes, threads),
    task scheduler, system calls and interrupt routines, memory management, file
    systems and I/O.
  \end{rSubsection}

  % \begin{rSubsection}{Teaching assistant}{2020}{Computer Architectures and Operating Systems}{Prof.\ Gerardo Pelosi}
  % \item Held 29 hours of exercise lectures for the Operating Systems part. Among other topics addressed:  parallel programming (processes, threads), Linux intro, task scheduler, memory management, file systems and I/O
  % \end{rSubsection}
%   \begin{rSubsection}{Teaching assistant}{2022}{Informatica (per Aerospaziali)}{Prof.\ Gerardo Pelosi}
%   \item Held 18 hours of exercise lectures. Among the topics addressed:
%     Boolean logic and basics of C programming  
%   \end{rSubsection}
%   \begin{rSubsection}{Teaching assistant}{2021}{Computer Architectures and Operating Systems}{Prof.\ Gerardo Pelosi}
%   \item Held 34 hours of exercise lectures for the Operating Systems part. Among other topics addressed:  parallel programming (processes, threads), Linux intro, task scheduler, memory management, file systems and I/O
%   \end{rSubsection}

% \begin{rSubsection}{Teaching assistant}{2020}{Computer Architectures and Operating Systems}{Prof.\ Gerardo Pelosi}
% \item Held 29 hours of exercise lectures for the Operating Systems part. Among other topics addressed:  parallel programming (processes, threads), Linux intro, task scheduler, memory management, file systems and I/O
% \end{rSubsection}

\begin{rSubsection}{Teaching tutor}{2019}{Informatica (per Ambientali)}{Prof.\ Andrea Bonarini}
\item Theory lectures and laboratory exercises on the C programming language.
% https://www11.ceda.polimi.it/schedaincarico/schedaincarico/controller/scheda_pubblica/SchedaPublic.do?&evn_default=evento&c_classe=691950&polij_device_category=DESKTOP&__pj0=0&__pj1=ee13b0b6c0f983f39edcd5af2ad25bd3
\end{rSubsection}

\begin{rSubsection}{Teaching tutor}{2018}{Computer Architectures and Operating Systems}{Prof.ssa Anna Maria Antola}
\item Theory lectures and lab exercises regarding both the architectures of
  modern computers (ranging from the assembly language to the logic gates) and
  the structure of an operating system (including the theory of parallel
  programming and threads management in Linux)
% https://www11.ceda.polimi.it/schedaincarico/schedaincarico/controller/scheda_pubblica/SchedaPublic.do?&evn_default=evento&c_classe=667442&polij_device_category=DESKTOP&__pj0=0&__pj1=f7cded5163ff00a70c340961c9ce685c
\end{rSubsection}
\end{rSection}
\vfill
\ifpublic{%
    \input{gdpr_en}
    \input{gdpr_it}
  }
\fi
\end{document}

% Add reviewer ICISSP 2023
% Add reviewer ICCAD 2021